When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-04-20 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
typo

To investigate the apparent group difference between the SVs of participants with NFC scores below and above the median in higher $n$-back levels, we computed an rmANOVA with the within-factor level (1 to 4) and the between-factor NFC group (below/above median).
There was no main effect of NFC group (`r apa_print(explor_model)$full_result$nfcmedian`, `r apa_print(explor_BF)$table[2,"statistic"]`), but a main effect of the $n$-back level (`r apa_print(explor_model)$full_result$level`, `r apa_print(explor_BF)$table[1,"statistic"]`) and an interaction (`r apa_print(explor_model)$full_result$nfcmedian_level`).
Post-hoc tests for the main effect of level showed that Svs were lower for the more difficult $n$-back level in each paired contrast except for 1- versus 2-back.
Post-hoc tests for the interaction effect showed that the NFC groups only had a significant difference in SVs for 4-back, where participants below the NFC median had lower scores (`r apa_print(pairs(explor_emm_interact))$full_result$X4_High_low`).
Despite not reaching significance, 1-back was the only level in which participants with NFC scores above the median seemed to have lower SVs than those with scores below the median (`r apa_print(pairs(explor_emm_interact))$full_result$X1_High_low`).
The full results of this exploratory analysis of NFC group differences can be found in Table S.16 and S.17 in the Supplementary Material.

>>>>

To investigate the apparent group difference between the SVs of participants with NFC scores below and above the median in higher $n$-back levels, we computed an rmANOVA with the within-factor level (1 to 4) and the between-factor NFC group (below/above median).
There was no main effect of NFC group (`r apa_print(explor_model)$full_result$nfcmedian`, `r apa_print(explor_BF)$table[2,"statistic"]`), but a main effect of the $n$-back level (`r apa_print(explor_model)$full_result$level`, `r apa_print(explor_BF)$table[1,"statistic"]`) and an interaction (`r apa_print(explor_model)$full_result$nfcmedian_level`).
Post-hoc tests for the main effect of level showed that SVs were lower for the more difficult $n$-back level in each paired contrast except for 1- versus 2-back.
Post-hoc tests for the interaction effect showed that the NFC groups only had a significant difference in SVs for 4-back, where participants below the NFC median had lower scores (`r apa_print(pairs(explor_emm_interact))$full_result$X4_High_low`).
Despite not reaching significance, 1-back was the only level in which participants with NFC scores above the median seemed to have lower SVs than those with scores below the median (`r apa_print(pairs(explor_emm_interact))$full_result$X1_High_low`).
The full results of this exploratory analysis of NFC group differences can be found in Table S.16 and S.17 in the Supplementary Material.
